Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-06-06 manuscript/main.tex
Update forecast snapshots to make forecasts from latest data
As of June 6, the latest H3N2 data were collected up to the beginning of
April. This commit uses forecasts made from April 1, 2020 to April 1, 2021 for a
more realistic comparison with how forecasts are made elsewhere in the
manuscript (i.e., from timepoints where all data are available).

After confirming the coefficients for our best model of HI antigenic novelty and mutational load, we inspected forecasts of H3N2 clades from January 2020 to 2021 using data available up through January 17, 2020.
Of the three major currently circulating clades, our model predicted growth of the clades A1b/131K and 3c3.A and decline of all other clades (Fig.~\ref{fig:nextstrain_forecasts}).
Four months after those forecasts, the subclades of A1b/131K represented 40\% of the global H3N2 population an increase from an estimated 35\% frequency in January.
The 3c3.A clade increased slightly in global frequency from 13\% to 15\%, in that time.
To aid with identification of potential vaccine candidates for the next season, we annotated strains in the phylogeny by their estimated distance to the future based on our best model (Fig.~\ref{fig:nextstrain_distance_to_future}).

\begin{figure}[htb]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/nextstrain-forecasts.png}
  \caption{
    Snapshot of live forecasts on nextstrain.org from our best model (HI antigenic novelty and mutational load) for January 2021.
    The observed frequency trajectories for currently circulating clades are shown up to January 2020.
    Our model forecasts growth of the clades A1b/131K and 3c3.A and decline of all other major clades.
  }
  \label{fig:nextstrain_forecasts}
  \end{center}
\end{figure}

>>>>

After confirming the coefficients for our best model of HI antigenic novelty and mutational load, we inspected forecasts of H3N2 clades using all data available up through June 6, 2020.
Consistent with an average two-month lag between data collection and submission, the most recent data were collected up to April 1, 2020 and made our forecasts from this timepoint to April 1, 2021.
Of the five major currently circulating clades, our model predicted growth of the clades 3c3.A and A1b/94N and decline of clades A1b/135K, A1b/137F, and A1b/197R (Fig.~\ref{fig:nextstrain_forecasts}).
To aid with identification of potential vaccine candidates for the next season, we annotated strains in the phylogeny by their estimated distance to the future based on our best model (Fig.~\ref{fig:nextstrain_distance_to_future}).

\begin{figure}[htb]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/nextstrain-forecasts.png}
  \caption{
    Snapshot of live forecasts on nextstrain.org from our best model (HI antigenic novelty and mutational load) for April 1, 2021.
    The observed frequency trajectories for currently circulating clades are shown up to April 1, 2020.
    Our model forecasts growth of the clades 3c3.A and A1b/94N and decline of all other major clades.
  }
  \label{fig:nextstrain_forecasts}
  \end{center}
\end{figure}
